The development of abstract concepts in children's early lexical networks

### 2019-02-27 CMCL/ms.Rmd
ms

---
title: "The development of abstract concepts in the early lexical network"

@@

abstract: 
    "How do children learn abstract concepts such as animal vs. artefact? Previous research suggests that such concepts can be derived using cues from the language they hear around them, e.g., word co-occurrence.  We propose that such information can be integrated in the evolving lexical network, and higher-level organization can be identified bottom-up as the dense components in this network. We found that early abstract categories develop simultaneously thanks to the children's word trajectory which favors the exploration of the global conceptual space."

@@

```{r, libraries}
library(png)
library(dplyr)
library(plyr)
library(broom)
#library(tidyr)
library(purrr)
library(langcog)
library(ggplot2)
library(grid)
library(lme4)
library(lmerTest)
library(ggthemes)
library(ggplot2)
library(xtable)
```

@@

Concepts are the building blocks of ideas. For example, the thought "birds are animals" requires the knowledge of both the concept "birds" and the concept "animal". They enable inductive reasoning and predictive inferences which guide behavior and explanation (Murphy, 2002). 
-->
One of the central challenges in cognitive development is to understand how concepts develop \cite{carey2009,keil1992,gopnik1997}. Of particular interest is the case of abstract concepts which have non-obvious shared properties such as "animal" and "artefacts". For example, a cat and a bird are perceptually quite different but they share some fundamental properties (e.g., breathing, feeding, and reproducing) which make them animals, and which set them apart from  the category of artefacts. In such cases learning requires, at least in part, cultural/linguistic cues which provide information beyond what can be obtained through the senses \cite{gelman2009,harris2012,csibra2009}

One way children's conceptual learning can benefit from the language they hear around them is through word co-occurrence. For example, one can learn an abstract concept (e.g., animal) simply by observing how its instances (e.g., "cat" and "bird") go together in speech. This is a plausible learning strategy. On the one hand, experimental research has shown that children track co-occurrence statistics \cite{saffran1996}. On the other hand, inspection of the caregiver’s input shows that it contains rich co-occurrence information about various abstract concepts \cite{huebner2018}.

What remains to be investigated is the way abstract concepts develop from the interaction of the children's learning mechanisms and the structure of their linguistic input. We study this development and compare it to two hypothetical developmental scenarios. On the first, learning starts by exploring the global conceptual structure; categories are refined simultaneously over development (we call this mechanism exploration-based learning). On the second scenario, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another (we call this mechanism exploitation-based learning).

The paper is organized as follows. First we describe the research strategy. In brief, we represented the developing lexicon as an evolving network and we used word co-occurrence in parent speech as a measure of words' relatedness. We operationalized high-level concepts as the highly interconnected components of the network.  Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and we compare this pattern to the development induced by the exploration-based and exploitation-based mechanisms. Finally, we discuss the findings in light of previous research.

```{r network, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=5, fig.height=8, fig.cap = "Network obtained using a sample of nouns in CDI data (nodes), and co-occurrence-based similarity from a corpus of child-directed speech (edges). Colors indicate highly interconnected clusters identified using unsupervised network community detection. The clusters correspond, overall, to four higher-level concepts: animal, food, clothes, and artefacts."}

@@

The networks' nodes were nouns form  Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version \cite{fenson94}. Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child directed speech CHILDES \cite{macwhinney2014}, using Word2Vec algorithm \cite{mikolov2013}.

First, we constructed the end-state network based on a subset of CDI data. This subset was made of nouns belonging to a diversity of semantic categories. Items of this subset (named "uni_lemmas" in the WordBank database) were translated across the languages used in this study, allowing us to account for cross-linguistic variability. Second, to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.

## Identifying high-level concepts in a network

We assume that high-level concepts correspond to clusters of highly interconnected nodes in the networks. We identified such clusters using  WalkTrap \cite{pons2006}, an unsupervised community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network. Figure \ref{fig:network} shows the outcome of cluster identification in the end-state network. The algorithm obtained four major clusters corresponding to the categories of clothes, food, animal and artefacts. We refer to this end-state clustering as $\mathcal{C}^*$. To examine developmental change in the conceptual organization, we run the cluster identification algorithm at each month of acquisition $t$, and we compare the resulting clustering, noted $\mathcal{C}_t$, to that of the end-state $\mathcal{C}^*$. The method of this comparison is detailed below.

@@

@@

We examined how higher-order concepts develop under the children's real word learning trajectory. We compared this development to the development induced by an exploration- and an exploitation-like learning. To construct the real word learning trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}.

The exploration-based learning was instantiated as a uniform sampling from the end-state vocabulary. The exploitation-based learning had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster. After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.\footnote{Note that the way we instantiated the exploitation-based learning is not fully unsupervised, but we were more interested in modeling extreme cases to which real learning can be compared.}
<!--
Since we are interested in the cross-linguistic study of development, we started by investigating the degree to which languages vary in their normative order of word learning. To this end, we calulated the pairwise Kendall rank correlation coefficient between languages, and we comapre it to the same measure obtained by comparing trajectories in different languages to random orderings.  The corresponding distributions, shown in Figure XX, do not overlap indicating that languages are more similar to each other than to random word orderings. The between-language distribution also shows there to be susbtantial cross-linguitc variability since the values are smaller than 1 (i.e., perfect correlation).
-->

@@

```{r hi}
#Models

#m1_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_precision_to_last' & randomization != "random_aoa"),
#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

##Test of convergence
#(From: https://github.com/lme4/lme4/issues/120)
#relgrad <- with(m1_precision@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

#saveRDS(m1_precision, "model_1.rds")
#xl_precision <- readRDS("model_1.rds")

#m2_precision <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_precision_to_last' & randomization != "within_last_clustering"),
#           control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))

#saveRDS(m2_precision, "model_2.rds")
#xp_precision <- readRDS("model_2.rds")

##Test of convergence
#relgrad <- with(xp_precision@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

#xl_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_recall_to_last' & randomization != "random_aoa"),
#                     control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

#saveRDS(xl_recall, "xl_recall.rds")
#xl_recall <- readRDS("xl_recall.rds")

#m2_recall <- lmer(value ~ age *  randomization + (age *  randomization | language) + (1 | n_clusters),
#           data = subset(all, measure =='pair_recall_to_last' & randomization != "within_last_clustering"),
#          control=lmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 1000000)))

#saveRDS(m2_recall, "model_recall_2.rds")
#xp_recall <- readRDS("model_recall_2.rds")

#relgrad <- with(xp_recall@optinfo$derivs,solve(Hessian,gradient))
#max(abs(relgrad))

#xl_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_precision))), "effect") %>%
#  mutate(sampling = "exploitation", score = "precision")
#xp_prec_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_precision))), "effect") %>%
#  mutate(sampling = "exploration", score = "precision")
#xl_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xl_recall))), "effect") %>%
#  mutate(sampling = "exploitation", score = "recall")
#xp_recall_coef <- tibble::rownames_to_column(as.data.frame(coef(summary(xp_recall))), "effect") %>%
#  mutate(sampling = "exploration", score ="recall")

#coef_all <- xl_prec_coef %>%
#  bind_rows(xp_prec_coef) %>%
#  bind_rows(xl_recall_coef) %>%
#  bind_rows(xp_recall_coef)

#feather::write_feather(coef_all, "../saved_data/coef_all.feather")
coef_all <- feather::read_feather("../saved_data/coef_all.feather")

p_val <- function(val) {
  if(val < 0.001) 
    {'< 0.001'} 
  else if(val < 0.01)
    {'<0.01'} 
  else if(val < 0.05)
    {'<0.05'} 
  else {paste('=', round(val,2))}
}

#Age 
age_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")],2)

age_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")],2)

age_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")],2)

age_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")],2)

age_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")]

age_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")]

age_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age"  &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")]

age_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="age" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")]

#Real vs. exploration

diff_xl_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")],2)

diff_xp_prec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")],2)

diff_xl_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")],2)

diff_xp_rec_co <- round(coef_all$Estimate[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")],2)

diff_xl_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="precision")]

diff_xp_prec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="precision")]

diff_xl_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationwithin_last_clustering" &
                                                  coef_all$sampling=="exploitation" &
                                                  coef_all$score =="recall")]

diff_xp_rec_p <- coef_all$'Pr(>|t|)'[which(coef_all$effect=="randomizationrandom_aoa" &
                                                  coef_all$sampling=="exploration" &
                                                  coef_all$score =="recall")]

@@

We first compared the real conceptual development to the one induced by exploration-based learning. To this end, we fit a mixed-effect regression using age and learning (real vs. exploration-based) as fixed effects, and using language and number of fixed clusters as random effects accounting for the nested structure of the data. Real and exploration-based patterns of conceptual developmental were indistinguishable for both precision ($\beta =$ `r diff_xp_prec_co`, $p$ `r p_val(diff_xp_prec_p)`) and recall ($\beta =$ `r diff_xp_rec_co`, $p$ `r p_val(diff_xp_rec_p)`).

Similarly, we compared real conceptual development to exploitation-based learning. Using a similar regression, we found a difference in both precision ($\beta =$ `r diff_xl_prec_co`, $p$ `r p_val(diff_xl_prec_p)`) and recall ($\beta =$ `r diff_xl_rec_co`, $p$ `r p_val(diff_xl_rec_p)`). Exploitation-base learning had generally higher precision, indicating there to be less false positive pairs. This result is due to the fact that we sampled instances from a same category. However, the same type of learning had lower recall, indicating there to be less false negative pairs. This second result was due to the fact that sampling from a same category leads to clusterings that are finer in their conceptual granularity than the end-state.

@@

This paper asks whether children can learn abstract concepts based on word co-occurrence in the language they hear around them. We found that, when using co-occurrence information in the developing lexical network, several high-level concepts such as "animal", "artefact", "food" and "clothes" emerge bottom-up as clusters of highly inter-connected nodes. In addition, these categories develop simultaneously thanks to the children's word learning trajectory which tends to favor the exploration of the global conceptual landscape rather than the exploitation and refinement of one specific category at time.

The development of the higher-level conceptual structure seems to be unaffected by the order with which words are acquired (as long as this order approximates a uniform/exploration-like sampling), suggesting that the process of conceptual development can accommodate a wide range of word learning trajectories without qualitative change in the higher order organization. For example, whether acquisition start first with the words "cat" and "banana" or with the words "cow" and "potato" does not qualitatively affect the higher-level organization involving "animal" and "food". This property is important as it suggests, for instance, that development may be resilient to variability in the children's linguistic input \cite{slobin2014,hart1995}.

@@

That said, these developmental changes were not necessarily related to specific concepts (since the patterns were similar when we randomized the order of word learning). Instead, this finding suggests that differentiation and coalescence of word pairs in our data are related to the change in the vocabulary size across development: As more words are added to their lexical network, learners may approximate better the underlying conceptual organization of the mature lexicon, and would make less categorization errors. Indeed, research in network science indicates that properties of a real networks become more distorted as the size of a sampled sub-network decreases \cite{leskovec2006}.

One limitation of this study is that we used the normative age of acquisition, computed using different children at different age groups. This choice was due to the cross-sectional nature of available CDI data. Though such a measure has been widely used to study important aspects of the early lexical network \cite{hills2009,stella2017,storkel2009}, it only applies at the population level. In our case, though we found that average concept development is driven more by an exploration-based mechanism, some individual children may display an exploitation-like behavior. For example, prior knowledge about dinosaurs may enable the learning of new dinosaur-related words more easily \cite{chi1983}.

In sum, this work provided a quantitative account of how abstract concepts can emerge from the interaction of the children's learning mechanism and the properties of their linguistic input. One important direction for future work is to investigate the extent to which the correlational findings obtained in this study (e.g., the identity of categories formed across development or the fact that categorization errors decrease with the size of the lexicon) can be corroborated by controlled behavioral experiments.

@@

If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case? This looks like an artefact of the clustering algorithm with smaller size data? Should discuss this with Isaac. Also, what is an exmaple of a clustering $\mathcal{C}_t$ for a smaller size: are some clusters totally empty?)

>>>>

---
title: "The development of abstract concepts in children's early lexical networks"

@@

abstract: 
    "How do children learn abstract concepts such as animal vs. artifact? Previous research has suggested that such concepts can partly be derived using cues from the language children hear around them. Following this suggestion, we propose a model where we represent the children's developing lexicon as an evolving network. The nodes of this network are based on vocabulary knowledge as reported by parents, and the edges between pairs of nodes are based on the probability of their co-occurrence in a corpus of child-directed speech. We found that several abstract categories can be identified as the dense components in such networks. In addition, these categories develop simultaneously, rather than sequentially, thanks to the children's word learning trajectory which favors the exploration of the global conceptual space."

@@

```{r, libraries}
library(png)
library(dplyr)
library(tidyr)
library(plyr)
library(broom)
#library(tidyr)
library(purrr)
library(langcog)
library(ggplot2)
library(grid)
library(lme4)
library(lmerTest)
library(ggthemes)
library(ggplot2)
library(xtable)
```

@@

Concepts are the building blocks of ideas. For example, the thought "birds are animals" requires the knowledge of both the concept "birds" and the concept "animal". They enable inductive reasoning and predictive inferences which guide behavior and explanation (Murphy, 2002). 
-->
One of the central challenges in cognitive development is to understand how concepts develop \cite{carey2009,keil1992,gopnik1997}. Of particular interest is the case of abstract concepts which have non-obvious shared properties such as "animal" and "artifact". For example, a cat and a bird are perceptually quite different but they share some fundamental properties (e.g., breathing, feeding, and reproducing) which make them animals (as opposed to artifacts). In such cases, learning requires in part cultural/linguistic cues which provide information beyond what can be obtained through the senses \cite{gelman2009,harris2012,csibra2009}.

One way children's conceptual learning can benefit from the language they hear around them is through word co-occurrence. For example, one can learn an abstract concept (e.g., animal) simply by observing how its instances (e.g., "cat" and "bird") go together in speech. Indeed, previous work has shown that the caregiver’s input contains rich co-occurrence information about various abstract concepts \cite{huebner2018}. This work, however, has explored the conceptual space from an adult perspective (using the words uttered by the caregivers).  Here we explore how abstract concepts may develop from the children's perspective, investigating how their word learning trajectory influences the higher-level organization.

<!--On the other hand, children can track co-occurrence statistics \cite{saffran1996} and there is evidence that they use co-occurrence to make category-based generalization \cite{fisher2011,matlen2015}. 
Here we investigate the way abstract concepts may develop from the interaction of the children developing lexicon and co-occurrence information in the caregiver's speech. 
-->
We study development in light of two hypothetical models. On the first, called the simultaneous model, learning starts by exploring the global conceptual structure; categories are refined simultaneously over development. On the second, called the sequential model, learning starts by exploring a small region of the conceptual space (e.g., the category "animals") and only after the refinement of this category, does the learner move to another.

The paper is organized as follows. First, we describe the research strategy. In brief, we represented the developing lexicon as an evolving network and we used word co-occurrence in parent speech as a measure of words' relatedness. We operationalized abstract concepts as the highly interconnected components of the network.  Second, we explore how the pattern of children's word learning influences higher-level conceptual development, and whether this development corresponds to a simultaneous or a sequential conceptual growth.

```{r network, fig.env = "figure*", fig.pos = "h", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.width=5, fig.height=8, fig.cap = "Network obtained using a sample of nouns in CDI data (nodes), and co-occurrence-based similarity from a corpus of child-directed speech (edges). Colors indicate highly interconnected clusters identified using unsupervised network community detection. The clusters correspond, overall, to four higher-level concepts: animal, food, clothes, and artifacts."}

@@

The networks' nodes were nouns from Wordbank \cite{frank2017}, an open repository aggregating cross-linguistic developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist, Toddler version \cite{fenson94}. Pairs of nouns were linked by weighted edges representing their semantic similarity derived based on co-occurrence in the corpus of child-directed speech CHILDES \cite{macwhinney2014}, using Word2Vec algorithm \cite{mikolov2013}.

First, we constructed the end-state network based on a subset of CDI nouns named "uni_lemmas" in the WordBank database. We used this subset since its items are translated across several languages, allowing us to account for cross-linguistic variability. We used the ten languages studied in \newcite{braginsky}. The size of this subset varied from XX in English (representing X% of total nouns in this language) to XX in XX (representing X% of total nouns). Second, in order to study development towards the end-state, we constructed a different network at each month, based on the nouns that have been learned by that month.

## Identifying abstract concepts in a network

We assume that abstract concepts correspond to clusters of highly interconnected nodes in the networks. We identified such clusters using  WalkTrap \cite{pons2006}, an unsupervised community detection algorithm based on the fact that a random walker tends to be trapped in dense parts of a network. Figure \ref{fig:network} shows the outcome of cluster identification in the end-state network. The algorithm obtained four major clusters corresponding to the categories of clothes, food, animal and artifacts. We refer to this end-state clustering as $\mathcal{C}^*$. To examine developmental change in the conceptual organization, we ran the cluster identification algorithm at each month of acquisition $t$, and we compared the resulting clustering, noted $\mathcal{C}_t$, to that of the end-state $\mathcal{C}^*$. The method of this comparison is detailed below.

@@

all_sum_corr <- all_sum %>%
  as.data.frame() %>%
  select(-ci_lower, -ci_upper) %>%
  spread(randomization, mean) %>%
  group_by(measure) %>%
  dplyr::summarise(sim = round(cor(Real, Exploration)^2, 2),
            seq = round(cor(Real, Exploitation)^2, 2))

r_sim_prec <- all_sum_corr$sim[which(all_sum_corr$measure=="Precision")]
r_sim_rec <- all_sum_corr$sim[which(all_sum_corr$measure=="Recall")]

r_seq_prec <- all_sum_corr$seq[which(all_sum_corr$measure=="Precision")]
r_seq_rec <- all_sum_corr$seq[which(all_sum_corr$measure=="Recall")]

@@

We examined how abstract concepts develop under the children's real word learning trajectory. To construct this trajectory, we used the normative age of acquisition, that is, the age at which a word is produced by at least 50% of children in each language \cite{goodman2008}. We compared this development to the development induced by a simultaneous model and the development induced by a sequential model.

The simultaneous model was instantiated as a uniform sampling across time from the end-state vocabulary. The sequential model had the additional constraint of sampling from one category at a time: the first word is selected randomly from one cluster, subsequent words are sampled from the same cluster. After all words from this cluster are used, a word from a different cluster is chosen, and the same process is repeated until all clusters are covered.\footnote{Note that the way we instantiated the sequential model is not fully unsupervised, but we were more interested in modeling extreme cases to which real learning can be compared.}
<!--
Since we are interested in the cross-linguistic study of development, we started by investigating the degree to which languages vary in their normative order of word learning. To this end, we calulated the pairwise Kendall rank correlation coefficient between languages, and we comapre it to the same measure obtained by comparing trajectories in different languages to random orderings.  The corresponding distributions, shown in Figure XX, do not overlap indicating that languages are more similar to each other than to random word orderings. The between-language distribution also shows there to be susbtantial cross-linguitc variability since the values are smaller than 1 (i.e., perfect correlation).
-->

@@

@@

The simultaneous model mimics closely the patterns of real conceptual development, explaining almost all the variance in mean precision  ($R^2 =$ `r r_sim_prec`) and recall ($R^2 =$ `r r_sim_rec`). In contrast, the sequential model had generally a higher precision, i.e., it induced less false positive pairs. This result is due to the fact that we sampled instances from a same category. However, the same model had generally lower recall scores, i.e., it induced more false negative pairs. This second result was due to the fact that sampling from a same category leads to clusterings that are finer in their conceptual granularity than the end-state. As a consequence of this discrepancy with respect to real development, the sequential model explained less variance than the simultaneous model did in both the mean precision ($R^2 =$ `r r_seq_prec`) and recall ($R^2 =$ `r r_seq_rec`).

@@

Can children learn abstract concepts based on word co-occurrence in the language they hear around them? Previous work has shown that child-directed speech contains information about several abstract concepts \cite{huebner2018}. Here we investigated when and how this information becomes available to children as their lexical network grows. We found that even with a small lexicon, several high-level concepts such as "animal", "artifact", "food" and "clothes" emerge bottom-up as clusters of highly interconnected nodes in the network. Furthermore,  compared with a model that posited sequential learning, we found that these categories tended to emerge in concert with one another.

<!--thanks to the children's word learning trajectory which favor the exploration of the global conceptual landscape rather than the exploitation and refinement of one specific category at a time. -->

The development of the higher-level conceptual structure seems to be unaffected by the order with which words are acquired (as long as this order approximates a uniform sampling from the end-state lexicon), suggesting that the process of conceptual development can accommodate a wide range of word learning trajectories without a qualitative change in the higher-level organization. For example, whether acquisition starts first with the words "cat" and "banana" or with the words "cow" and "potato" does not qualitatively affect the higher-level organization involving "animal" and "food". This property is important as it suggests, for instance, that development is resilient to variability in the children's linguistic input \cite{slobin2014,hart1995}.

@@

That said, these developmental changes were not necessarily related to specific concepts (since the patterns were similar when we randomized the order of word learning). Instead, this finding suggests that differentiation and coalescence of word pairs in our data are related to the change in the vocabulary size across development: As more words are added to their lexical network, learners may approximate better the underlying conceptual organization of the mature lexicon and would make fewer categorization errors. Indeed, research in network science indicates that properties of a real network become more distorted as the size of a sampled sub-network decreases \cite{leskovec2006}.

One limitation of this study is that we used the normative age of acquisition, computed using different children at different age groups. This choice was due to the cross-sectional nature of available CDI data. Though such a measure has been widely used to study important aspects of the early lexical networks \cite{hills2009,stella2017,storkel2009}, it only applies at the population level. In our case, though we found that concepts develop simultaneously, individual children may display, at least locally, a sequential-like behavior. For example, prior knowledge about dinosaurs may enable the learning of new dinosaur-related words more easily \cite{chi1983}.

In sum, this work provided a quantitative account of how abstract concepts can emerge from the interaction of the children's emerging vocabulary and the properties of their linguistic input. One important direction for future work is to investigate the extent to which the correlational findings obtained in this study (e.g., the identity of categories formed across development or the fact that categorization errors decrease with the size of the lexicon) can be corroborated by controlled behavioral experiments.

@@

If precision is lower early on, it means that initial concepts are not differentiated enough, that is, pairs that should belong to different concpets are intially lamped together (false positives), despite the fact that we forced the same number of clsuters in both $\mathcal{C}_t$ and $\mathcal{C}^*$ (Why is this the case? This looks like an artifact of the clustering algorithm with smaller size data? Should discuss this with Isaac. Also, what is an exmaple of a clustering $\mathcal{C}_t$ for a smaller size: are some clusters totally empty?)
